---
title: "COVID impact on endurance athletes"
author: "Félix Boudry"
date: "`r Sys.Date()`"
documentclass: article
classoption: oneside
lang: en-US
output:
  html_document: 
    toc: yes
    number_section: yes
    fig_caption: yes
    number_sections: yes
  word_document:
    toc: yes
    number_sections: 4
    fig_caption: yes
  pdf_document: 
    toc: yes
    toc_depth: 4
    number_sections: yes
    fig_caption: yes
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	error = TRUE,
	message = FALSE,
	warning = FALSE
)
# Import libraries
library(knitr)
library(tibble)
library(janitor)
library(dplyr)
library(CatEncoders)
library(ggplot2)
library(psych)
library(kableExtra)
library(plyr)
library(gridExtra)
```

```{r Sourcing}
rm(list = ls())
source(file = "Scripts/Import.R")
source(file = "Scripts/Descriptive.R")
source(file = "Scripts/Transform.R")
```

# Information

**Hypothesis** : Endurance-trained athletes would have more difficulties
returning to training at their best level after a COVID-19 infection.

# Population

Some anthropometric data about the population in this study:

In the population kept in this study there are
**`r data_trans$sex_count$feminin`** womens and
**`r data_trans$sex_count$masculin`** mens and all of the
**`r nrow(my_data$raw_data$completed)`** subjects were infected by COVID-19.

```{r}
kable(my_results$antrop_data$completed) %>%
  kable_styling(bootstrap_options = c("striped"))
print(my_results$antrop_plots$completed)
```

There data will be analysed with several subcategories:
- Sex
- Age
- IMC?
- Pathology
- Endurance trained
- Training volume
- Training modalities

# Endurance

## Training

```{r}
ggplot(mapping = aes(x = my_data$raw_data$completed$endurance_sport)) +
  geom_bar() +
  xlab("Endurance trained") +
  scale_x_discrete(labels = c("Yes", "No")) +
  ggtitle("Number of endurance trained and not trained subjects")
```

In the studied population, **`r data_trans$endurance_count$oui`** are endurance
trained athletes.

Subject's professions are shown below:

```{r}
ggplot(mapping = aes(y = my_data$raw_data$completed$profession)) +
  geom_bar() +
  ylab(label = "Profession") +
  ggtitle(label = "Subject's profession")
```

Various types of activities are done by the subjects. (potential errors during 
computing!)

```{r}
ggplot(mapping = aes(y = data_trans$sports)) +
  geom_bar() +
  ylab(label = "Profession") +
  ggtitle(label = "Subject's profession")
```

## COVID symptomes

```{r}
mapply(
  FUN = function(my_column, my_colname) {
    ggplot(mapping = aes(x = my_column)) +
      geom_bar(aes(fill = my_data$raw_data$completed$endurance_sport)) +
      geom_text(aes(label = after_stat(count)), stat = "count", vjust = 1) +
      ggtitle(my_colname) +
      labs(fill = "Endurance")
  },
  my_column = data_trans$covid_symp,
  my_colname = colnames(data_trans$covid_symp),
  SIMPLIFY = FALSE
) %>% 
  marrangeGrob(nrow = 2, ncol = 3)
```

## Post COVID symptomes

```{r}
mapply(
  FUN = function(my_column, my_colname) {
    ggplot(mapping = aes(x = my_column)) +
      geom_bar(aes(fill = my_data$raw_data$completed$endurance_sport)) +
      geom_text(aes(label = ..count..), stat = "count", vjust = 2) +
      ggtitle(my_colname) +
      labs(fill = "Endurance")
  },
  my_column = data_trans$post_covid_symp,
  my_colname = colnames(data_trans$post_covid_symp),
  SIMPLIFY = FALSE
) %>% 
  marrangeGrob(nrow = 2, ncol = 3)
```

## Training resumption

```{r}
ggplot(my_data$raw_data$completed, aes(
  x = reorder(duration_to_training, duration_to_training, function(x)
    -length(x))
)) +
  geom_bar(aes(fill = my_data$raw_data$completed$endurance_sport)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Duration to training resumption") +
  labs(fill = "Endurance")
```

## Training symptoms

```{r}
mapply(
  FUN = function(my_column, my_colname) {
    ggplot(mapping = aes(x = my_column)) +
      geom_bar(aes(fill = my_data$raw_data$completed$endurance_sport)) +
      geom_text(aes(label = ..count..), stat = "count", vjust = 2) +
      ggtitle(my_colname) +
      labs(fill = "Endurance")
  },
  my_column = data_trans$training_symptoms,
  my_colname = colnames(data_trans$training_symptoms),
  SIMPLIFY = FALSE
) %>% 
  marrangeGrob(nrow = 2, ncol = 2)

mapply(
  FUN = function(my_column, my_colname) {
    ggplot(mapping = aes(x = my_column)) +
      geom_histogram(aes(fill = my_data$raw_data$completed$endurance_sport)) +
      # geom_text(aes(label = ..count..), stat = "count", vjust = 2) +
      ggtitle(my_colname) +
      labs(fill = "Endurance")
  },
  my_column = data_trans$training_symptoms_notes,
  my_colname = colnames(data_trans$training_symptoms_notes),
  SIMPLIFY = FALSE
) %>% 
  marrangeGrob(nrow = 2, ncol = 2)

ggplot(data = my_data$raw_data$completed, aes(
  x = reorder(difficulties_duration, difficulties_duration, function(x)
    -length(x))
)) +
  geom_bar() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Difficulties duration at training")
```

## Medication

Needed?







