---
params:
  new_title: "My title"
title: "`r params$new_title`"
author: "Félix Boudry"
date: "`r Sys.Date()`"
documentclass: article
classoption: oneside
lang: en-US
output:
  html_document: 
    toc: yes
    number_section: yes
    fig_caption: yes
    number_sections: yes
  word_document:
    toc: yes
    number_sections: 4
    fig_caption: yes
  pdf_document: 
    toc: yes
    toc_depth: 4
    number_sections: yes
    fig_caption: yes
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 12,
  fig.height = 6
)
# Import libraries
require(tidyverse)
require(knitr)
require(janitor)
require(gridExtra)
```

```{r Configuration}
rm(list = setdiff(
  x = ls(),
  y = c("my_var",
        "gen_env",
        "my_population")
))
```

# Population description

## Anthropometrics

Presentation of the population studied.

In the population kept in this study there are
**`r my_results$num$results_antrop$population_values$sex$feminin`** womens and
**`r my_results$num$results_antrop$population_values$sex$masculin`** mens and all of the
**`r nrow(my_data)`** subjects were infected by COVID-19.

```{r Anthropometrics}
my_table_count(input = my_data$covid_test,
               my_colnames = c("Tests", "freq"))
my_table(input = my_results$num$results_antrop$antrop_values)
my_results$plots$plots_antrop$antrop_plots %>%
  marrangeGrob(ncol = 3, nrow = 1, top = NULL)
```

## Training

```{r}
my_results$plots$plots_training$training_plots[c("endurance_sport", "federal_license")] %>%
  marrangeGrob(nrow = 1, ncol = 2, top = NULL)
binary_proportions[c("endurance_sport", "federal_license")]
lapply(
  X = my_results$plots$plots_training$training_plots[c("train_volume", "train_sessions_week", "train_method")],
  FUN = function(x) {
    x + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
  }
) %>%
  marrangeGrob(nrow = 1, ncol = 2, top = NULL)
my_results$plots$plots_training$training_plots$what_sport +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```

In the studied population, **`r my_results$num$results_training$training_values$endurance_sport$oui`** are endurance
trained athletes.

## Professions

Subject's professions are shown below:

```{r}
my_results$plots$plots_antrop$population_plots$profession
```

## Pathologies

**`r count(my_data$pathology)[2, 2]`** have a known pathology.

```{r}
my_results$plots$plots_pathologies$pathologies_plots$pathology_description +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
my_results$plots$plots_pathologies$pathologies_plots$pathology_medication
```

# COVID impact on training

## COVID

### Symptoms

```{r}
my_results$plots$plots_covid$covid_symptoms_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "cough",
  "fever",
  "runny_nose",
  "headache",
  "sore_throat",
  "tired",
  "muscular_pain",
  "vomiting",
  "diarrhea",
  "breathlessness",
  "respiratory_difficulties",
  "other_symptoms"
)]
```

## Post COVID

### Symptoms

```{r}
my_results$plots$plots_post_covid$post_covid_infos_plots[c("after_symptoms", "restart_training")] %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$binary_proportions[c("after_symptoms", "restart_training")]
my_results$plots$plots_post_covid$post_covid_infos_plots$duration_to_training
my_results$continuous_results$duration_to_training
my_results$plots$plots_post_covid$post_covid_symptoms_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "after_cough",
  "after_fever",
  "after_runny_nose",
  "after_headache",
  "after_sore_throat",
  "after_tired",
  "after_muscular_pain",
  "after_vomiting",
  "after_diarrhea",
  "after_breathlessness",
  "after_respiratory_difficulties"
)]
my_results$plots$plots_post_covid$training_symptoms_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "training_tired",
  "training_respiratory_difficulties",
  "training_muscular_pain",
  "training_concentration_difficulties"
)]
my_results$plots$plots_post_covid$training_symptoms_notes_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$continuous_results[c(
  "training_tired_note",
  "training_respiratory_difficulties_note",
  "training_muscular_pain_note",
  "training_concentration_difficulties_note"
)]
my_results$plots$plots_post_covid$post_covid_difficulties_plots$difficulties_duration +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
my_results$continuous_results$difficulties_duration
my_results$plots$plots_post_covid$post_covid_difficulties_plots[-c(1, 6, 7)] %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "restart_training_medication",
  "respiratory_medication",
  "cortisone_medication",
  "vitamin_medication"
)]
```

```{r, fig.height=knitr::opts_chunk$get("fig.height")/2}
my_results$plots$plots_post_covid$post_covid_difficulties_plots[c(6, 7)] %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$binary_proportions$other_medication
my_results$continuous_results$medication_duration
```

### Training difficulties

```{r}
my_results$plots$plots_train_diff$training_types_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "high_intensity_training",
  "force_training",
  "endurance_training",
  "intermittent_training",
  "other_training"
)]
my_results$plots$plots_train_diff$training_difficulties_plots %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c("longer_recuperation",
                                "training_volume_back_normal")]
my_results$continuous_results[c(
  "modified_training_volume",
  "time_to_normal_training_volume",
  "endurance_training_more_difficult"
)]
```

### Hypoxia training

```{r}
my_results$plots$plots_hypoxia$hypoxia_plots[-c(7, 9)] %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$binary_proportions[c(
  "hypoxia_training",
  "after_hypoxia_training",
  "500-2000_hypoxia",
  "2000-3000_hypoxia",
  "3000-5500_hypoxia",
  "5500-more_hypoxia",
  "hypoxia_difficulties",
  "hypoxia_respiratory_difficulties"
)]
my_results$continuous_results$hypoxia_respiratory_difficulties_note
```

```{r fig.height=knitr::opts_chunk$get("fig.height")/2}
lapply(
  X = my_results$plots$plots_hypoxia$hypoxia_plots[c(7, 9)],
  FUN = function(x) {
    x + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
  }
) %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$continuous_results$hypoxia_duration
```

